Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-24 prop_iop.tex
prop_letter.tex Fix typo...

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectrum decomposition
\begin{equation}
\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
Then, 
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
 & = & \int X\rmd\bar{\mu}'\\
 & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
\end{eqnarray*}
\end{proof}

>>>>

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
Then, 
\begin{eqnarray*}
 &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
 & = & \int X\rmd\bar{\mu}'\\
 & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu'\left(\tau\left(P_{i}^{-}\right)\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu'\left(\tau\left(P_{i}^{+}\right)\right)\right]\\
 & = & \textrm{(Need to verify the detail, but seems correct...)}\\
 & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu\left(P_{i}^{+}\right)\right]\\
 & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{-}\right)+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{+}\right)\right]\\
 & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]
\end{eqnarray*}
\end{proof}
